The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-06-05 manuscript.Rmd
re-organize discussion about barcoding results

The proportion of species that have DNA barcodes available is relatively constant across the better studied phyla at the scale of the EEZ. It varies between 12% for bryozoans to 28% for cnidarians. The proportions for species known to occur in the Gulf of Mexico are usually similar than for the US, while typically a higher fraction of species from the Pacific Northwest are available. Geographic information is missing for most records (`r format_output(100*stat_bold$p_no_coords)`% of the `r format(stat_bold$n_total_records)` BOLD records analyzed here have no geographic coordinates information associated with them), and many marine invertebrate species are known to be cryptic complexes that are not as widely distributed as previously thought. Therefore specimens identified under the same species but sampled in distant locations, could represent cryptic species. It is thus crucial to ensure that accurate geographic information is provided when DNA barcodes are published, and that additional samples are collected, to capture more accurately their geographic range and the extent of their genetic diversity. This cryptic diversity is reflected in the fact that `r stat_bold$n_spp_multi_bin` species out of `r stat_bold$n_spp` include more than 1 BIN (BOLD Index Number, operational taxonomic units that closely resemble species [@Ratnasingham2013]).

>>>>

The proportion of species that have DNA barcodes available is relatively constant across the better studied phyla at the scale of the EEZ. It varies between 12% for bryozoans to 28% for cnidarians. The proportions for species known to occur in the Gulf of Mexico are usually similar than for the US, while typically a higher fraction of species from the Pacific Northwest are available. In 2010, it was estimated that a global scale, less than 10% of the species for each marine phylum had been sequenced [@Radulovici2010], suggesting that the US fauna is generally better characterized than the rest of the world, combined with many other species have been sequenced since this report.

Using the fraction of known species that have a barcode as a yard stick of the progress made is not sufficient. Many marine invertebrate species are known to be cryptic complexes that are not as widely distributed as currently reported [@Knowlton2000,@Meyer2005-evolution]. Therefore specimens identified under the same species but sampled in distant locations, could represent cryptic species. Geographic information is missing for most records (`r format_output(100*stat_bold$p_no_coords)`% of the `r format(stat_bold$n_total_records)` BOLD records analyzed here have no geographic coordinates information associated with them). It is thus crucial to ensure that accurate geographic information is provided when DNA barcodes are published, and that enough samples for each species are sequenced, to capture more accurately their geographic range and the extent of their genetic diversity. This cryptic diversity is also at least partially reflected in the fact that `r stat_bold$n_spp_multi_bin` species out of `r stat_bold$n_spp` include more than 1 BIN (BOLD Index Number, operational taxonomic units that closely resemble species [@Ratnasingham2013]).
